# Results

```{r co2eq, include = FALSE}

SevoCO2eq = c(
    waste = 140 # @Nielsen2024
    ## TODO manufacturing
)

TotalUsedWeightSev <- sum(agc$TotalUsedWeightSev)
TotalRecoveredSev <- NA # TODO, response Zeosys needed
CaptureEfficiency <- TotalRecoveredSev / TotalUsedWeightSev
```

During the study period we consumed `r TotalUsedWeightSev` gram Sevoflurane
where `r TotalRecoveredSev` could recovered (capture efficiency
`r .pct(CaptureEfficiency, prec = ".0")`).

```{r table1, echo = FALSE, message = FALSE}
theme_gtsummary_compact(font_size = 8L)

tbl_cases <- agc |>
    mutate(OR = ifelse(OR == 21, "21 (ENT)", "25 (Neurosurgery)")) |>
    select(
        OR,
        TotalCases,
        TotalCasesTiva,
        TotalCasesSev,
        TotalDurationCases,
        TotalDurationCasesTiva,
        TotalDurationCasesSev,
        AvgDurationSev
    ) |>
    dplyr::mutate_at(vars(matches("Duration")), function(x)x / 60) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            TotalCases ~ "continuous",
            TotalCasesTiva ~ "continuous",
            TotalCasesSev ~ "continuous",
            TotalDurationCases ~ "continuous",
            TotalDurationCasesTiva ~ "continuous",
            TotalDurationCasesSev ~ "continuous",
            AvgDurationSev ~ "continuous"
        ),
        label = list(
            TotalCases ~ "Number of cases",
            TotalCasesTiva ~ "Number of total intravenous anaesthesia cases",
            TotalCasesSev ~ "Number of inhaled anaesthesia cases",
            TotalDurationCases ~ "Total duration of all cases [h]",
            TotalDurationCasesTiva ~ "Total duration of total intravenous anaesthesia [h]",
            TotalDurationCasesSev ~ "Total duration of inhaled anaesthesia [h]",
            AvgDurationSev ~ "Average duration of inhaled anaesthesia [h]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_overall() |>
    add_p()

tbl_weights <- agc |>
    select(
        OR,
        InitialWeight,
        FinalWeight,
        WeightGain,
        InVivoMassTransfer
    ) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            InitialWeight ~ "continuous",
            FinalWeight ~ "continuous",
            WeightGain ~ "continuous",
            InVivoMassTransfer ~ "continuous"
        ),
        label = list(
            InitialWeight ~ "Initial weight [g]",
            FinalWeight ~ "Final weight [g]",
            WeightGain ~ "Weight gain [g]",
            InVivoMassTransfer ~ "In vivo mass transfer [%]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_overall() |>
    add_p()

tbl_sevo_consumption <- agc |>
    select(
        OR,
        TotalUsedVolumeSev,
        TotalUsedWeightSev,
        UsedVolumePerHourSev,
        UsedWeightPerHourSev
    ) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            TotalUsedVolumeSev ~ "continuous",
            TotalUsedWeightSev ~ "continuous",
            UsedVolumePerHourSev ~ "continuous",
            UsedWeightPerHourSev ~ "continuous"
        ),
        label = list(
            TotalUsedVolumeSev ~ "Total used sevoflurane volume [mL]",
            TotalUsedWeightSev ~ "Total used sevoflurane weight [g]",
            UsedVolumePerHourSev ~ "Average used sevoflurane volume per hour [mL/h]",
            UsedWeightPerHourSev ~ "Average used sevoflurane weight per hour [g/h]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_overall() |>
    add_p()

tbl_stack(
    tbls = list(
        tbl_cases, tbl_sevo_consumption, tbl_weights
    ),
    group_header = c(
        "Case summary",
        "Sevoflurane consumption",
        "Anaesthetic gas canister weights"
    )
) |>
## indent variable names and missing
modify_table_styling(columns = "label", text_format = "indent") |>
modify_table_styling(
    rows = row_type %in% c("missing", "level"),
    columns = "label",
    text_format = "indent2"
) |>
modify_spanning_header(c("stat_1", "stat_2") ~ "**Operating rooms**") |>
modify_caption(
    paste0(
        "ENT: ear, nose and throat surgery; ",
        "Characteristics of all ", nrow(agc), " anaesthetic gas canisters. ",
        "Cases, duration etc. are given as per canister."
    )
)
```

Assuming a greenhouse warming potential over a 100 year time horizont (GWP~100~) of `r SevoCO2eq["waste"]` we saved
`r CaptureEfficiency * SevoCO2eq["waste"]` g carbon dioxide equivalents (CO~2~eq) [@Nielsen2024].

TODO: calc saved CO2-eq
taxonomy introduced in @Gandhi2024
