# Results

```{r counts, include = FALSE}
nCases <- tapply(agc$TotalCases, agc$OR, sum)
nCasesSev <- tapply(agc$TotalCasesSev, agc$OR, sum)
```


```{r co2eq, include = FALSE}

SevoCO2eq = c(
    waste = 140, # @Nielsen2024
    manufacturing = 143.2928 # @Hu2021, supplement 1-s2.0-S0921344921000185-mmc2.xlsx, Table "CO2-Eq (Route-C):E37" 886.5143 and Table "CO2-Eq (Route-E):E38" 143.2928 - Route B
    # 20.625
    # Presentation Baxter LCA: Life Cycle Assessment of Anaesthetic Gas Capture in the Operating Room using ContraFluran Tom Costelloe, Michael Collins, Doyin Oladele and Simon Aumônier 25/01/2022
    # source should be: "Life Cycle Greenhouse Gas Emissions of Anaesthetic Drugs", Sherman et al. Anesthesia & Analgesia. 114(5):1086-1090, May 2012; could not find direct number; maybe could be calculated with LCA software given the ingredients
)

CONTRAfluranCO2eq <- 66.6 # @Costelloe2022, Scenario UK, page 14

AGSSkWh <- 0.1 # @Schuster2023
kWhCO2eq <- 0.485 # @Schuster2023

TotalUsedWeightSev <- sum(agc$TotalUsedWeightSev)
TotalWeightGain <- sum(agc$WeightGain)
TotalRecoveredSev <- TotalWeightGain * 0.85 #NA # TODO, response ZeoSys needed
CaptureEfficiency <- TotalRecoveredSev / TotalUsedWeightSev
AGC14EstimatedUsedWeightSev <- sum(flowvapor$Consumption)

agc$ProportionalCaptureEfficiency <-
    (agc$WeightGain / TotalWeightGain * TotalRecoveredSev) /
    agc$TotalUsedWeightSev

TotalDurationCases <- sum(agc$TotalDurationCases)

TotalCO2eq <- c(
    CONTRAfluran = unname(
        # manufacturing
        TotalUsedWeightSev * SevoCO2eq["manufacturing"] +
        # waste
        (TotalUsedWeightSev - TotalRecoveredSev) * SevoCO2eq["waste"] +
        # CONTRAfluran production/transportion/desorption
        (TotalWeightGain * CONTRAfluranCO2eq) -
        # saving
        TotalRecoveredSev * SevoCO2eq["manufacturing"]
    ),
    AGSS =
        TotalUsedWeightSev * sum(SevoCO2eq) +
        TotalDurationCases * AGSSkWh * kWhCO2eq
)

ORCO2eq <- tapply(agc, agc$OR, function(aa) {
    UsedSev <- sum(aa$TotalUsedWeightSev)
    RecoSev <- TotalRecoveredSev * sum(aa$WeightGain) / TotalWeightGain

    # manufacturing
    UsedSev * SevoCO2eq["manufacturing"] +
    # waste
    (UsedSev - RecoSev) * SevoCO2eq["waste"] +
    # CONTRAfluran production/transportion/desorption
    (sum(aa$WeightGain) * CONTRAfluranCO2eq) -
    # saving
    RecoSev * SevoCO2eq["manufacturing"]
})
```

```{r table1, echo = FALSE, message = FALSE}
theme_gtsummary_compact(font_size = 8L)

tbl_cases <- agc |>
    mutate(OR = ifelse(OR == ORnames[1],
        paste(ORnames[1], "(ENT)"), paste(ORnames[2], "(Neurosurgery)"))) |>
    select(
        OR,
        TotalCases,
        TotalCasesSev,
        TotalDurationCasesSev,
        AvgDurationSev
    ) |>
    dplyr::mutate_at(vars(matches("Duration")), function(x)x / 60) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            TotalCases ~ "continuous",
            TotalCasesSev ~ "continuous",
            TotalDurationCasesSev ~ "continuous",
            AvgDurationSev ~ "continuous"
        ),
        label = list(
            TotalCases ~ "Number of cases",
            TotalCasesSev ~ "Number of inhaled anaesthesia cases",
            TotalDurationCasesSev ~ "Total duration of inhaled anaesthesia [h]",
            AvgDurationSev ~ "Average duration of inhaled anaesthesia [h]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_p()

tbl_weights <- agc |>
    select(
        OR,
        InitialWeight,
        FinalWeight,
        WeightGain,
        InVivoMassTransfer,
        ProportionalCaptureEfficiency
    ) |>
    dplyr::mutate(
        ProportionalCaptureEfficiency = ProportionalCaptureEfficiency * 100
    ) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            InitialWeight ~ "continuous",
            FinalWeight ~ "continuous",
            WeightGain ~ "continuous",
            InVivoMassTransfer ~ "continuous",
            ProportionalCaptureEfficiency ~ "continuous"
        ),
        label = list(
            InitialWeight ~ "Initial weight [g]",
            FinalWeight ~ "Final weight [g]",
            WeightGain ~ "Weight gain [g]",
            InVivoMassTransfer ~ "In vivo mass transfer [%]",
            ProportionalCaptureEfficiency ~ "Proportional capture efficiency [%]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_p()

tbl_weights_overall <- add_overall(tbl_weights)

tbl_sevo_consumption <- agc |>
    select(
        OR,
        TotalUsedVolumeSev,
        TotalUsedWeightSev,
        UsedVolumePerHourSev,
        UsedWeightPerHourSev
    ) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            TotalUsedVolumeSev ~ "continuous",
            TotalUsedWeightSev ~ "continuous",
            UsedVolumePerHourSev ~ "continuous",
            UsedWeightPerHourSev ~ "continuous"
        ),
        label = list(
            TotalUsedVolumeSev ~ "Total used sevoflurane volume [mL]",
            TotalUsedWeightSev ~ "Total used sevoflurane weight [g]",
            UsedVolumePerHourSev ~ "Average used sevoflurane volume per hour inhaled anaesthesia [mL/h]",
            UsedWeightPerHourSev ~ "Average used sevoflurane weight per hour inhaled anaesthesia [g/h]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_p()

tbl1 <- tbl_stack(
    tbls = list(
        tbl_cases, tbl_sevo_consumption, tbl_weights
    ),
    group_header = c(
        "(A) Case summary",
        "(B) Sevoflurane consumption",
        "(C) Anaesthetic gas canister characteristics"
    )
) |>
## indent variable names and missing
modify_table_styling(columns = "label", text_format = "indent") |>
modify_table_styling(
    rows = row_type %in% c("missing", "level"),
    columns = "label",
    text_format = "indent2"
) |>
modify_spanning_header(c("stat_1", "stat_2") ~ "**Operating rooms**") |>
modify_caption(
    paste0(
        "ENT: ear, nose and throat surgery; ",
        "Characteristics of all ", nrow(agc), " anaesthetic gas canisters. ",
        "Cases, duration etc. are given as per canister."
    )
)
tbl1
```

## Sevoflurane consumption and capture efficiency

During the `r .as.word(ceiling(difftime(max(periods$End), min(periods$Start), units = "weeks")))` weeks study period we investigated a total of `r sum(nCases)` anaesthesia cases.
Of these `r .pct(sum(nCasesSev) / sum(nCases), prec = ".0")` received volatile
anaesthetics at a total duration of `r sprintf("%.0f", sum(agc$TotalDurationCasesSev) / 60)` h
with an average sevofluran consumption of `r sprintf("%.1f", median(agc$UsedWeightPerHourSev))` g/h.
Comparing the two ORs, we found a large and significant difference in the total
used sevoflurane, which is due to differences in the ratio of patients receiving
volatile anaesthetics and the differences in the duration of anaesthesia (Table \@ref(tab:table1)A).

In total `r sprintf("%.1f kg", TotalUsedWeightSev / 1000)` sevoflurane was used
and `r sprintf("%.1f kg", TotalRecoveredSev / 1000)` could be recaptured
(capture efficiency `r .pct(CaptureEfficiency, prec = ".0")`).

While median weight and weight gain of the AGCs did not differ between the two
ORs, we observed a large and significant difference of the
in vivo mass transfer, which was at
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]`
due to the significantly different sevoflurane consumption in both ORs (Table \@ref(tab:table1)B and C).
Thus, assuming the same proportion of sevoflurane could be accounted for the relative
weight gain of each AGC, the proportional capture efficiency, differed
significantly between the two ORs, with
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]` (Table \@ref(tab:table1)C).

The details of each AGC can be found in Supplemental Table \@ref(tab:tableagc).

## Weight loss

Before sending all AGCs to ZeoSys we weighed them again and found an almost
linear decrease in weight over time of around `r round(fit.weigth.loss$coefficients * 1000)` mg per day
(Figure \@ref(fig:plot-weight-lost) and Supplemental Section \@ref(weight-lost-during-storage))).

```{r plot-weight-lost, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 8, echo = FALSE, fig.cap = "Weight loss of the anaesthetic gas canisters during storage."}
old.par <- par(no.readonly = TRUE)
on.exit(par(old.par))

xlim <- range(agc$DaysStored)
ylim <- range(agc$LostWeight)

col.fit <- "#0f0f0f"

plot(
    NA,
    xlim = xlim, ylim = ylim,
    axes = FALSE, xlab = "", ylab = ""
)
points(agc$DaysStored, agc$LostWeight, col = viridisLite::cividis(1), pch = 20)
abline(fit.weigth.loss, lty = "dashed", lwd = 2, col = col.fit)
text(
    x = max(agc$DaysStored), y = max(agc$LostWeight),
    labels =
        bquote(R^2*"="*.(round(summary(fit.weigth.loss)$r.squared, 3))),
    adj = c(1.5, -0.2), col = col.fit, cex = 1.2

)
title(main = "WEIGHT LOSS OF THE ANAESTHETIC GAS CANISTERS DURING STORAGE", col.main = "#808080", adj = 0L)
title(xlab = "DAYS STORED", adj = 0L, col.lab = "#808080")
title(ylab = "WEIGHT LOST [g]", adj = 1L, col.lab = "#808080")
axis(1L, col = "#808080", col.axis = "#808080", lwd.ticks = 0)
axis(2L, col = "#808080", col.axis = "#808080", lwd.ticks = 0, las = 2)
```
