# Results


```{r table1, echo = FALSE, message = FALSE}
tbl1
```


## Sevoflurane consumption and capture efficiency

During the `r .as.word(ceiling(difftime(max(periods$End), min(periods$Start), units = "weeks")))` week study period we investigated a total of `r sum(nCases)` anaesthesia cases.
Of these `r .pct(sum(nCasesSev) / sum(nCases), prec = ".0")` received volatile
anaesthetics at a total duration of `r sprintf("%.0f", sum(agc$TotalDurationCasesSev) / 60)` h
with an average sevofluran consumption of `r sprintf("%.1f", median(agc$UsedWeightPerHourSev))` g.h^-1^.
Comparing the two ORs, we found a large and significant difference in the total
used sevoflurane, which is due to differences in the ratio of patients receiving
volatile anaesthetics and the differences in the duration of anaesthesia (Table \@ref(tab:table1)A).

In total `r sprintf("%.1f kg", TotalUsedWeightSev / 1000)` sevoflurane was used
and `r sprintf("%.1f kg", TotalRecoveredSev / 1000)` could be recaptured
(capture efficiency `r .pct(CaptureEfficiency, prec = ".0")`).

While median weight and weight gain of the AGCs did not differ between the two
ORs, we observed a large and significant difference in the
in vivo mass transfer, which was at
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]`
due to the significantly different sevoflurane consumption in both ORs (Table \@ref(tab:table1)B and C).
Thus, assuming the same proportion of sevoflurane could be accounted for the relative
weight gain of each AGC, the proportional capture efficiency differed
significantly between the two ORs, with
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]` (Table \@ref(tab:table1)C).

The details of each AGC can be found in Supplemental Table \@ref(tab:tableagc).

## Weight loss

Before sending all AGCs to ZeoSys we weighed them again and found an almost
linear decrease in weight over time of around `r round(fit.weigth.loss$coefficients * 1000)` mg per day
(Figure \@ref(fig:plot-weight-lost) and Supplemental Section \@ref(weight-lost-during-storage))).

```{r plot-weight-lost, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 8, echo = FALSE, fig.cap = "Weight loss of the anaesthetic gas canisters during storage."}
old.par <- par(no.readonly = TRUE)
on.exit(par(old.par))

xlim <- range(agc$DaysStored)
ylim <- range(agc$LostWeight)

col.fit <- "#0f0f0f"

plot(
    NA,
    xlim = xlim, ylim = ylim,
    axes = FALSE, xlab = "", ylab = ""
)
points(agc$DaysStored, agc$LostWeight, col = viridisLite::cividis(1), pch = 20)
abline(fit.weigth.loss, lty = "dashed", lwd = 2, col = col.fit)
text(
    x = max(agc$DaysStored), y = max(agc$LostWeight),
    labels =
        bquote(R^2*"="*.(round(summary(fit.weigth.loss)$r.squared, 3))),
    adj = c(1.5, -0.2), col = col.fit, cex = 1.2

)
title(main = "WEIGHT LOSS OF THE ANAESTHETIC GAS CANISTERS DURING STORAGE", col.main = "#808080", adj = 0L)
title(xlab = "DAYS STORED", adj = 0L, col.lab = "#808080")
title(ylab = "WEIGHT LOST [g]", adj = 1L, col.lab = "#808080")
axis(1L, col = "#808080", col.axis = "#808080", lwd.ticks = 0)
axis(2L, col = "#808080", col.axis = "#808080", lwd.ticks = 0, las = 2)
```
