# Results


```{r table1, echo = FALSE, message = FALSE}
tbl1
```


## Sevoflurane consumption and capture efficiency

We observed a total of `r sum(nCases)` anaesthesia cases
during the `r .as.word(ceiling(difftime(max(periods$End), min(periods$Start), units = "weeks")))` week study period,
of which `r .pct(sum(nCasesSev) / sum(nCases), prec = ".0")` received VAs
at a total duration of `r sprintf("%.0f", sum(agc$TotalDurationCasesSev) / 60)` h.

A total of `r sprintf("%.1f kg", TotalUsedWeightSev / 1000)` sevoflurane was used
and `r sprintf("%.1f kg", TotalRecoveredSev / 1000)` could be recaptured
(capture efficiency `r .pct(CaptureEfficiency, prec = ".0")`).
Sevoflurane attributed `r .pct(RatioSevoWeight, prec = ".1")` of CONTRAfluran's weight gain.
The remaining `r .pct(1 - RatioWeightLoss, prec = ".1")` were water (and only traces of metabolic products like acetone, Compound A-E, etc.).

Comparing the two ORs, we found a large and significant difference in the total
sevoflurane used, which is partly due to differences in the ratio of patients receiving
VAs and the variations in the duration of anaesthesia (Table \@ref(tab:table1)A and B).

While the median weight gain of the AGCs did not differ between the two
ORs, we observed a large and significant difference in the
*in vivo* mass transfer, which was at
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]`
due to the significantly different sevoflurane consumption in the two ORs (Table \@ref(tab:table1)B and C).
Thus, assuming the same proportion of sevoflurane could be accounted for the relative
weight gain of each AGC, the proportional capture efficiency differed
significantly between the two ORs, with
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]` (Table \@ref(tab:table1)C).

The details of each AGC can be found in Supplemental Table \@ref(tab:tableagc).

## Weight loss

The `r paste0(nrow(agc), " AGCs were stored for ", .medLU(agc$DaysStored), " days")`
in median (lower and upper quartile) in our hospital and additional
`r round(difftime(ymd("20241202"), ymd("20240409"), units = "days"))` days at
ZeoSys before the desorption process.
During the whole storage period we observed a loss of
`r .medLU(agc$LostWeight2)` gram in median (lower and upper quartile) for each
AGC and of `r TotalWeightLoss` gram in total.
This corresponds to `r .pct(RatioWeightLoss)`.
(Figure \@ref(fig:plot-weight-lost)).

```{r plot-weight-lost, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 8, echo = FALSE, fig.cap = "Weight loss of the anaesthetic gas canisters during storage. The dots represent the weight loss of each individual anaesthetic gas canister for the days after exhaustion before shipping and desorption. The gray lines connect the same anaesthetic gas canisters measured at the two different time points."}
old.par <- par(no.readonly = TRUE)
on.exit(par(old.par))

xlim <- range(weights$DaysStored)
ylim <- c(0, 20)

col.fit <- "#0f0f0f"

plot(
    NA,
    xlim = xlim, ylim = ylim,
    axes = FALSE, xlab = "", ylab = ""
)
segments(
    weights$DaysStored[1:20], weights$LostWeight[1:20],
    weights$DaysStored[21:40], weights$LostWeight[21:40],
    col = "#20202020", lwd = 0.5
)
points(
    weights$DaysStored, weights$LostWeight, col = viridisLite::cividis(1),
    pch = 19
)
text(
    c(
        max(weights$DaysStored[1:20]) / 2,
        min(weights$DaysStored[21:40]) +
        (max(weights$DaysStored[21:40]) - min(weights$DaysStored[21:40])) / 2
    ),
    19.5,
    labels = toupper(
        paste("before", c("shipping", "desorption"))
    ),
    col = "#808080",
    cex = 0.8
)
#xx <- seq(0, max(weights$DaysStored), length.out = 100)
#lines(
#    xx, predict(fit.weight.loss, newdata = data.frame(DaysStored = xx)),
#    lty = "dashed", lwd = 2, col = col.fit
#)
#text(
#    x = max(weights$DaysStored), y = max(weights$LostWeight),
#    labels =
#        bquote(R^2*"="*.(round(summary(fit.weight.loss)$r.squared, 3))),
#    adj = c(1.5, -0.2), col = col.fit, cex = 1.2
#
#)
title(main = "WEIGHT LOSS OF THE ANAESTHETIC GAS CANISTERS DURING STORAGE", col.main = "#808080", adj = 0L)
title(xlab = "DAYS STORED", adj = 0L, col.lab = "#808080")
title(ylab = "WEIGHT LOST [g]", adj = 1L, col.lab = "#808080")
axis(1L, col = "#808080", col.axis = "#808080", lwd.ticks = 0)
axis(2L, col = "#808080", col.axis = "#808080", lwd.ticks = 0, las = 2)
```
