# Results

```{r counts, include = FALSE}
ORnames <- paste0("OR", unique(agc$OR))
nCases <- tapply(agc$TotalCases, agc$OR, sum)
nCasesTiva <- tapply(agc$TotalCasesTiva, agc$OR, sum)
nCasesSev <- tapply(agc$TotalCasesSev, agc$OR, sum)
pCasesSev <- nCasesSev / nCases
```


```{r co2eq, include = FALSE}

SevoCO2eq = c(
    waste = 140, # @Nielsen2024
    manufacturing = 143.2928 # @Hu2021, supplement 1-s2.0-S0921344921000185-mmc2.xlsx, Table "CO2-Eq (Route-C):E37" 886.5143 and Table "CO2-Eq (Route-E):E38" 143.2928 - Route B
    # 20.625
    # Presentation Baxter LCA: Life Cycle Assessment of Anaesthetic Gas Capture in the Operating Room using ContraFluran Tom Costelloe, Michael Collins, Doyin Oladele and Simon Aumônier 25/01/2022
    # source should be: "Life Cycle Greenhouse Gas Emissions of Anaesthetic Drugs", Sherman et al. Anesthesia & Analgesia. 114(5):1086-1090, May 2012; could not find direct number; maybe could be calculated with LCA software given the ingredients
)

CONTRAfluranCO2eq <- 66.6 # @Costelloe2022, Scenario UK, page 14

AGSSkWh <- 0.1 # @Schuster2023
kWhCO2eq <- 0.485 # @Schuster2023

TotalUsedWeightSev <- sum(agc$TotalUsedWeightSev)
TotalWeightGain <- sum(agc$WeightGain)
TotalRecoveredSev <- TotalWeightGain * 0.85 #NA # TODO, response ZeoSys needed
CaptureEfficiency <- TotalRecoveredSev / TotalUsedWeightSev
AGC14EstimatedUsedWeightSev <- 112.5 # consumption temporary based on Draeger connect 112.5 g; recalculation when logbook available

agc$ProportionalCaptureEfficiency <-
    (agc$WeightGain / TotalWeightGain * TotalRecoveredSev) /
    agc$TotalUsedWeightSev

TotalDurationCases <- sum(agc$TotalDurationCases)

TotalCO2eq <- c(
    CONTRAfluran = unname(
        # manufacturing
        TotalUsedWeightSev * SevoCO2eq["manufacturing"] +
        # waste
        (TotalUsedWeightSev - TotalRecoveredSev) * SevoCO2eq["waste"] +
        # CONTRAfluran production/transportion/desorption
        (TotalWeightGain * CONTRAfluranCO2eq) -
        # saving
        TotalRecoveredSev * SevoCO2eq["manufacturing"]
    ),
    AGSS =
        TotalUsedWeightSev * sum(SevoCO2eq) +
        TotalDurationCases * AGSSkWh * kWhCO2eq
)

ORCO2eq <- tapply(agc, agc$OR, function(aa) {
    UsedSev <- sum(aa$TotalUsedWeightSev)
    RecoSev <- TotalRecoveredSev * sum(aa$WeightGain) / TotalWeightGain

    # manufacturing
    UsedSev * SevoCO2eq["manufacturing"] +
    # waste
    (UsedSev - RecoSev) * SevoCO2eq["waste"] +
    # CONTRAfluran production/transportion/desorption
    (sum(aa$WeightGain) * CONTRAfluranCO2eq) -
    # saving
    RecoSev * SevoCO2eq["manufacturing"]
})
```

```{r table1, echo = FALSE, message = FALSE}
theme_gtsummary_compact(font_size = 8L)

tbl_cases <- agc |>
    mutate(OR = ifelse(OR == 21, "21 (ENT)", "25 (Neurosurgery)")) |>
    select(
        OR,
        TotalCases,
        TotalCasesTiva,
        TotalCasesSev,
        TotalDurationCases,
        TotalDurationCasesTiva,
        TotalDurationCasesSev,
        AvgDurationSev
    ) |>
    dplyr::mutate_at(vars(matches("Duration")), function(x)x / 60) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            TotalCases ~ "continuous",
            TotalCasesTiva ~ "continuous",
            TotalCasesSev ~ "continuous",
            TotalDurationCases ~ "continuous",
            TotalDurationCasesTiva ~ "continuous",
            TotalDurationCasesSev ~ "continuous",
            AvgDurationSev ~ "continuous"
        ),
        label = list(
            TotalCases ~ "Number of cases",
            TotalCasesTiva ~ "Number of total intravenous anaesthesia cases",
            TotalCasesSev ~ "Number of inhaled anaesthesia cases",
            TotalDurationCases ~ "Total duration of all cases [h]",
            TotalDurationCasesTiva ~ "Total duration of total intravenous anaesthesia [h]",
            TotalDurationCasesSev ~ "Total duration of inhaled anaesthesia [h]",
            AvgDurationSev ~ "Average duration of inhaled anaesthesia [h]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_p()

tbl_weights <- agc |>
    select(
        OR,
        InitialWeight,
        FinalWeight,
        WeightGain,
        InVivoMassTransfer,
        ProportionalCaptureEfficiency
    ) |>
    dplyr::mutate(
        ProportionalCaptureEfficiency = ProportionalCaptureEfficiency * 100
    ) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            InitialWeight ~ "continuous",
            FinalWeight ~ "continuous",
            WeightGain ~ "continuous",
            InVivoMassTransfer ~ "continuous",
            ProportionalCaptureEfficiency ~ "continuous"
        ),
        label = list(
            InitialWeight ~ "Initial weight [g]",
            FinalWeight ~ "Final weight [g]",
            WeightGain ~ "Weight gain [g]",
            InVivoMassTransfer ~ "In vivo mass transfer [%]",
            ProportionalCaptureEfficiency ~ "Proportional capture efficiency [%]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_p()

tbl_weights_overall <- add_overall(tbl_weights)

tbl_sevo_consumption <- agc |>
    select(
        OR,
        TotalUsedVolumeSev,
        TotalUsedWeightSev,
        UsedVolumePerHourSev,
        UsedWeightPerHourSev
    ) |>
    tbl_summary(
        by = OR,
        missing_text = "(Missing)",
        type = list(
            TotalUsedVolumeSev ~ "continuous",
            TotalUsedWeightSev ~ "continuous",
            UsedVolumePerHourSev ~ "continuous",
            UsedWeightPerHourSev ~ "continuous"
        ),
        label = list(
            TotalUsedVolumeSev ~ "Total used sevoflurane volume [mL]",
            TotalUsedWeightSev ~ "Total used sevoflurane weight [g]",
            UsedVolumePerHourSev ~ "Average used sevoflurane volume per hour [mL/h]",
            UsedWeightPerHourSev ~ "Average used sevoflurane weight per hour [g/h]"
        ),
        digits = all_continuous() ~ 1
    ) |>
    add_p()

tbl1 <- tbl_stack(
    tbls = list(
        tbl_cases, tbl_sevo_consumption, tbl_weights
    ),
    group_header = c(
        "Case summary",
        "Sevoflurane consumption",
        "Anaesthetic gas canister weights"
    )
) |>
## indent variable names and missing
modify_table_styling(columns = "label", text_format = "indent") |>
modify_table_styling(
    rows = row_type %in% c("missing", "level"),
    columns = "label",
    text_format = "indent2"
) |>
modify_spanning_header(c("stat_1", "stat_2") ~ "**Operating rooms**") |>
modify_caption(
    paste0(
        "ENT: ear, nose and throat surgery; ",
        "Characteristics of all ", nrow(agc), " anaesthetic gas canisters. ",
        "Cases, duration etc. are given as per canister."
    )
)
tbl1
```

The anaesthesia cases, sevoflurane consumption, and weights per AGC are
presented in Table \@ref(tab:table1).

During the `r .as.word(ceiling(difftime(max(periods$End), min(periods$Start), units = "weeks")))` weeks study period we had `r sum(nCases)` anaesthesia cases in total (`r paste0(ORnames, collapse = ", ")`).
In `r paste0(.pct(pCasesSev, prec=".0", symbol = c(FALSE, TRUE)), collapse = " and ")`
of cases an inhaled anaesthesia was used in `r paste0(ORnames, collapse = " and " )`.
The average duration of these inhaled anaesthesia cases of
`r .tbl(tbl_cases, "AvgDurationSev", column = "stat_1", pattern = "{median}")`
and
`r .tbl(tbl_cases, "AvgDurationSev", column = "stat_2", pattern = "{median}")` h and
the average sevofluran consumption of
`r .tbl(tbl_sevo_consumption, "UsedWeightPerHourSev", column = "stat_1", pattern = "{median}")`
and
`r .tbl(tbl_sevo_consumption, "UsedWeightPerHourSev", column = "stat_2", pattern = "{median}")`
g/h for `r paste0(ORnames, collapse = " and ")` differed significantly (both
`r .tbl(tbl_cases, "AvgDurationSev", column = "p.value")`).

In total `r sprintf("%.1f kg", TotalUsedWeightSev / 1000)` sevoflurane was used
and `r sprintf("%.1f kg", TotalRecoveredSev / 1000)` could be recovered
(capture efficiency `r .pct(CaptureEfficiency, prec = ".0")`).

The median weight of new and exhausted AGCs was
`r .tbl(tbl_weights_overall, "InitialWeight")` and
`r .tbl(tbl_weights_overall, "FinalWeight")` g, respectively.
This was a median (Q1, Q3) weight gain of `r .tbl(tbl_weights_overall, "WeightGain")` g.
However, the median in vivo mass transfer was significantly different with
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "InVivoMassTransfer", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]`
due to the significantly different sevoflurane consumption in both operating rooms.
Assuming the same proportion of sevoflurane could be accounted for the relative
weight gain of each AGC the proportional capture efficiency, with
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_1", pattern = "{median} %")` for `r ORnames[1]`
and
`r .tbl(tbl_weights, "ProportionalCaptureEfficiency", column = "stat_2", pattern = "{median} %")`  for `r ORnames[2]` was statistically different as well.
The details of each AGC can be found in Supplemental Table \@ref(tab:tableagc).

After removal of the last exhausted AGC, CH0100012088, in `r ORnames[2]`
the vapor was not refilled and the weigh difference of the sevoflurane bottle
not recorded.
Thats why we calculate the sevoflurane consumption data for the four last
anaesthesia cases as described in @Biro2015
(Supplemental Section \@ref(estimation-of-sevoflurane-consumption)).
They described an overestimation of the sevoflurane consumption by 7.6 %.
For our AGC CH0100012088 this would result in an error of
`r .pct((AGC14EstimatedUsedWeightSev * 0.076) / agc$TotalUsedWeightSev[agc$Id == "CH0100012088"], prec = ".2")`
and would just slightly underestimate the in vivo mass transfer and proportional
capture efficiency.

Before sending all AGCs to Zeosys we weighed them again and found an almost
linear decrease in weight over time of around `r round(fit.weigth.loss$coefficients * 1000)` mg per day
(Figure \@ref(fig:plot-weight-lost) and Supplemental Section \@ref(weight-lost-during-storage))).

```{r plot-weight-lost, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 8, echo = FALSE, fig.cap = "Weight loss during storage."}
old.par <- par(no.readonly = TRUE)
on.exit(par(old.par))

xlim <- range(agc$DaysStored)
ylim <- range(agc$LostWeight)

col.fit <- "#0f0f0f"

plot(
    NA,
    xlim = xlim, ylim = ylim,
    axes = FALSE, xlab = "", ylab = ""
)
points(agc$DaysStored, agc$LostWeight, col = viridisLite::cividis(1), pch = 20)
abline(fit.weigth.loss, lty = "dashed", lwd = 2, col = col.fit)
text(
    x = max(agc$DaysStored), y = max(agc$LostWeight),
    labels =
        bquote(R^2*"="*.(round(summary(fit.weigth.loss)$r.squared, 3))),
    adj = c(1.5, -0.2), col = col.fit, cex = 1.2

)
title(main = "WEIGHT LOSS DURING STORAGE", col.main = "#808080", adj = 0L)
title(xlab = "DAYS STORED", adj = 0L, col.lab = "#808080")
title(ylab = "WEIGHT LOST [g]", adj = 1L, col.lab = "#808080")
axis(1L, col = "#808080", col.axis = "#808080", lwd.ticks = 0)
axis(2L, col = "#808080", col.axis = "#808080", lwd.ticks = 0, las = 2)
```
