# Declarations

## Ethical approval

Research involving human subjects complied with all relevant national regulations and institutional policies, as well as the tenets of the Helsinki Declaration (as revised in 2013), and was approved by the ethics committee of the University Medicine Greifswald
(reference number: `r rmarkdown::metadata[["ethics_committee"]][["reference_number"]]`;
approval date: `r rmarkdown::metadata[["ethics_committee"]][["approval_date"]]`)

## Consent for publication

Not applicable.

## Availability of data and materials

The datasets generated and/or analysed during the current study are available in the zenodo repository,
`r bib <- bibtex::read.bib(frf("bibliography", "bibliography.bib")); bib[["vctordata"]]$url` @vctordata.

## Competing interests

```{r competing-interests, echo = FALSE, results = "asis"}
.drop_author_title <- function(x)gsub(",.*$", "", x)
.initials <- function(x)gsub("\\W*\\b(\\w)\\w*", "\\1", x)
authors <- unlist(rmarkdown::metadata$author, recursive = FALSE)

cois <- vapply(authors, "[[", "competing_interest", FUN.VALUE = NA_character_)

names(cois) <- .initials(.drop_author_title(names(cois)))
is_none <- cois == "none"

if (all(is_none)) {
    cat("All authors state no conflict of interest.")
} else if (all(!is_none)) {
    cat(paste(names(cois), cois))
} else {
    cat(
        paste(names(cois)[!is_none], cois[!is_none]),
        "The authors declare that they have no competing interests."
    )
}
```

## Funding

None.

## Author Contributions

```{r author-contributions, echo = FALSE, results = "asis"}
roles <- lapply(authors, "[[", "role")
nn <- lengths(roles)
ctbs <- data.frame(
    author = rep(names(roles), nn),
    contribution = unlist(roles),
    row.names = seq_len(sum(nn))
)
ctbs <- ctbs[order(ctbs$contribution, ctbs$author),]
l <- split(.initials(.drop_author_title(ctbs$author)), ctbs$contribution)
nms <- names(l)
actbs <- character(length(l))
## lapply/mapply is not working with .cli_text, even `force` doesn't help
for (i in seq_along(l)) {
    nm <- nms[i]
    txt <- l[[i]]
    actbs[i] <- paste0(nm, ": ", .cli_text("{txt}"), collapse = "; ")
}
cat(
    paste0(actbs, collapse = "; "),
    ". All authors have read and agreed to the published version",
    " of the manuscript.",
    sep = ""
)
```

## Acknowledgement

We thank Marco Reinke and Steffen Suermann from Draeger Medical Deutschland GmbH for exporting the Draeger connect data, the Draeger Perseus' logbooks and for helpful discussions about sevoflurane consumption.
Additonally, we like to thank Christian Ewers, managing director of ZeoSys medical, for reporting the amount of recovered sevoflurane and information about the desorption process.
