# Supplement

## Table of anaesthetic gas canisters

```{r tableagc, echo = FALSE, message = FALSE, caption = "Details of anaesthetic gas canisters."}
d <- agc;
d$Id[d$Id == "CH0100012088"] <-  "CH0100012088^\\*^"
d[c(
    "Id", "OR", "InitialWeight", "FinalWeight", "WeightGain",
    "LostWeight", "LostWeight2",
    "DaysStored", "DaysStored2",
    "TotalCases", "TotalCasesSev",
    "TotalDurationCases", "TotalDurationCasesSev", "AvgDurationSev",
    "TotalUsedWeightSev", "UsedWeightPerHourSev",
    "InVivoMassTransfer")] |>
    knitr::kable(
        digits = 1,
        col.names = c(
            "Id", "OR",
            "W~i~", "W~f~", "W~d~", "W~l~", "W~z~", "S", "Z",
            "N", "N~sev~",
            "D", "D~sev~", "D~avg~",
            "C~sev~", "C~avg~",
            "MT"
        ),
        caption = paste0(
            "Details of anaesthetic gas canisters. ",
            paste0(
                c(
                    "C~sev~: total sevoflurane used [g]",
                    "C~avg~: average sevoflurane used [g·h^-1^]",
                    "D: total duration [h]",
                    "D~sev~: total duration of sevoflurane cases [h]",
                    "D~avg~: average duration of sevoflurane cases [h]",
                    "Id: lot number",
                    "MT: in vivo mass transfer [%]",
                    "N: total number of anaesthesia cases",
                    "N~sev~: total number of sevoflurane cases",
                    "OR: operation room",
                    "S: days stored after exhausted before shipping",
                    "Z: days stored before desorption",
                    "W~d~: weight gain",
                    "W~f~: final weight when exhausted, directly after disconnection",
                    "W~i~: initial weight",
                    "W~l~: weight lost after exhausted and before shipping",
                    "W~z~: weight lost just before desorption",
                    paste0(
                        "^\\*^: the sevoflurane consumption of ",
                        sprintf("%.2f", AGC14EstimatedUsedWeightSev),
                        " g for the last four cases was estimated ",
                        "(\\@ref(estimation-of-sevoflurane-consumption))."
                    )
                ),
                collapse = "; "
            )
        )
    )
```


## Comparing sevoflurane consumption measurements

We weighed the sevoflurane
(SEVOrane, AbbVie Deutschland GmbH & Co. KG, Mainz, Germany) bottles
before and after filling of the Draeger D-Vapor 3000
(Draeger Medicine Deutschland GmbH, Luebeck, Germany)
vaporizer and record the difference.
Subsequently we determine the difference using the gold standard -
weighing the vaporizer before and after filling.
The bottles and the vaporizers were weighed with a Kern PCB 2500-2 scale
(Kern&Sohn GmbH, Balingen-Frommern; Germany; maximum weight = 2500 g; d = 0.01 g)
and a Kern PNJ 12000-M1 scale
(Kern&Sohn GmbH, Balingen-Frommern; Germany; maximum weight = 12000 g; d = 0.1 g),
respectively.

We did `r nrow(scales)` comparisons (`r 4 * nrow(scales)` weight measurements
in total) and found a mean difference of
`r sprintf("%.2f g (95 %% CI: %.2f, %.2f)", scalesMeanDiff, scalesCIMeanDiff[1L], scalesCIMeanDiff[2L])`.
The 95\ % limits of agreement are
`r sprintf("%.2f to %.2f g", scalesLADiff[1L], scalesLADiff[2L])`.

```{r plot-bland-altmann, dev = ifelse_is_docx("tiff", "png"), fig.width = 12, fig.height = 8, echo = FALSE, fig.cap = "Bland-Altman plot comparing weight methods for determination of sevoflurane consumption."}
old.par <- par(no.readonly = TRUE)
on.exit(par(old.par))

xlim <- range(scales$Avg)
ylim <- c(min(scalesLADiff, scales$Diff), max(scalesLADiff, scales$Diff))

plot(
    scales$Avg, scales$Diff,
    xlim = xlim, ylim = ylim,
    axes = FALSE, xlab = "", ylab = "",
    pch = 19,
    col = viridisLite::cividis(1)
)

abline(
    h = c(0, scalesMeanDiff, scalesLADiff),
    lty = c("dashed", "solid", "solid", "solid"),
    col = "#808080"
)

axis(1L, col = "#808080", col.axis = "#808080", lwd.ticks = 0)
axis(2L, col = "#808080", col.axis = "#808080", lwd.ticks = 0, las = 2)
title(main = "COMPARISON OF SEVOFLURANE CONSUMPTION MEASURMENTS", col.main = "#808080", adj = 0L)
title(xlab = "AVERAGE WEIGHT DIFFERENCE [g]", adj = 0L, col.lab = "#808080")
title(ylab = "DIFFERENCE BETWEEN WEIGHT MEASUREMENTS (VAPORIZER WEIGHT - BOTTLE WEIGHT) [g]", adj = 1L, col.lab = "#808080", cex.lab = 0.8)

text(
    max(scales$Avg) - strwidth("MEAN - 1.96 SD"),
    c(scalesMeanDiff, scalesLADiff),
    labels = toupper(
        c("MEAN", "MEAN - 1.96 SD", "MEAN + 1.96 SD")
    ),
    adj = c(0, 1.5),
    col = "#808080",
    cex = 0.8
)
```


## Estimation of sevoflurane consumption

After changing the last anaesthetic gas canister *CH0100012088* in `r ORnames[2]`,
the vaporizer was not refilled.
Therefore, we retrospectively calculated the sevoflurane consumption for the
last four anaesthesia cases utilising the user log entry provided by the Draeger
Perseus anaesthesia machine.
The calculation was done as described in Biro et al. with the following formula
[@Biro2015].

$$
agent\ consumption\ [g] = \frac{fresh\ gas\ flow\ [mL·min^{-1}] * vapor\ setting\ [Vol \%] *
anaesthesia\ duration\ [min]}{saturated\ gas\ volume\ [mL] * 100\ [Vol \%]} *
density\ [g·mL^{-1}]
$$

We used 184 mL as *saturated gas volume* [@Biro2015] and a density of
`r sevodensity` g·mL^-1^ for sevoflurane [@Hu2021].

```{r sevoflurane-consumption-estimation-agc14-tables, echo = FALSE}
knitr::kable(
    col.names = c("Case", "Time since vaporizer opened [min]",
                  "Fresh gas flow [l·min^-1^]",
                  "Vaporizer setting [Vol%]", "Duration [min]",
                  "Sevoflurane consumption [g]"),
    digits = 2,
    flowvapor,
    caption = paste0(
        "Overview of settings and consumption of the last four cases for ",
        "anaesthetic gas canister *CH0100012088*."
    )
)

knitr::kable(
    col.names = c("Case", "Total sevoflurane consumption [g]"),
    digits = 2,
    cbind(
        case = 1:4,
        tapply(flowvapor$Consumption, flowvapor$Case, sum)
    ),
    caption = paste0(
        "Sevoflurane consumption of the last four cases for ",
        "anaesthetic gas canister *CH0100009273*."
    )
)
```


## R session information


```{r sessioninfo}
sessionInfo()
```


## Git commit hash


```{r gitcommithash, echo = FALSE}
sprintf("Git commit revision: %s", system("git rev-parse HEAD", intern = TRUE))
```

