# Supplement

## Table of anaesthetic gas canisters

```{r tableagc, echo = FALSE, message = FALSE, caption = "Details of anaesthetic gas canisters."}
d <- agc;
d$Id[d$Id == "CH0100012088"] <-  "CH0100012088^\\*^"
d[c(
    "Id", "OR", "InitialWeight", "FinalWeight", "WeightGain",
    "LostWeight", "LostWeight2",
    "DaysStored", "DaysStored2",
    "TotalCases", "TotalCasesSev",
    "TotalDurationCases", "TotalDurationCasesSev", "AvgDurationSev",
    "TotalUsedWeightSev", "UsedWeightPerHourSev",
    "InVivoMassTransfer")] |>
    knitr::kable(
        digits = 1,
        col.names = c(
            "Id", "OR",
            "W~i~", "W~f~", "W~d~", "W~l~", "W~z~", "S", "Z",
            "N", "N~sev~",
            "D", "D~sev~", "D~avg~",
            "C~sev~", "C~avg~",
            "MT"
        ),
        caption = paste0(
            "Details of anaesthetic gas canisters. ",
            paste0(
                c(
                    "C~sev~: total sevoflurane used [g]",
                    "C~avg~: average sevoflurane used [g.h^-1^]",
                    "D: total duration [h]",
                    "D~sev~: total duration of sevoflurane cases [h]",
                    "D~avg~: average duration of sevoflurane cases [h]",
                    "Id: lot number",
                    "MT: in vivo mass transfer [%]",
                    "N: total number of anaesthesia cases",
                    "N~sev~: total number of sevoflurane cases",
                    "OR: operation room",
                    "S: days stored after exhausted before shipping",
                    "Z: days stored before desorption",
                    "W~d~: weight gain",
                    "W~f~: final weight when exhausted, directly after disconnection",
                    "W~i~: initial weight",
                    "W~l~: weight lost after exhausted and before shipping",
                    "W~z~: weight lost just before desorption",
                    paste0(
                        "^\\*^: the sevoflurane consumption of ",
                        sprintf("%.2f", AGC14EstimatedUsedWeightSev),
                        " g for the last four cases was estimated ",
                        "(\\@ref(estimation-of-sevoflurane-consumption))."
                    )
                ),
                collapse = "; "
            )
        )
    )
```

## Estimation of sevoflurane consumption

After changing the last AGC *CH0100012088* in OR25, the vaporizer was not refilled.
Therefore, we retrospectively calculated the sevoflurane consumption for the
last four anaesthesia cases utilising the user log entry provided by the Draeger
Perseus anaesthesia machine.
The calculation was done as described in @Biro2015.

```{r sevoflurane-consumption-estimation-agc14-tables, echo = FALSE}
knitr::kable(
    col.names = c("Case", "Time since vaporizer opened [min]",
                  "Fresh gas flow [l.min^-1^]",
                  "Vaporizer setting [Vol%]", "Duration [min]",
                  "Sevoflurane consumption [g]"),
    digits = 2,
    flowvapor,
    caption = paste0(
        "Overview of settings and consumption of the last four cases for ",
        "AGC *CH0100012088*."
    )
)

knitr::kable(
    col.names = c("Case", "Total sevoflurane consumption [g]"),
    digits = 2,
    cbind(
        case = 1:4,
        tapply(flowvapor$Consumption, flowvapor$Case, sum)
    ),
    caption = paste0(
        "Sevofluran consumption of the last four cases for ",
        "AGC *CH0100009273*."
    )
)
```

## R session information


```{r sessioninfo}
sessionInfo()
```


## Git commit hash


```{r gitcommithash, echo = FALSE}
sprintf("Git commit revision: %s", system("git rev-parse HEAD", intern = TRUE))
```

